PANCHANGE_data_merging

### 2020-10-26 PANNEURO_CFS_merge_script_WHO-pres.Rmd

# Import data
```{r export data}
glad <- read_rds(path = paste0(data_path, "/glad.rds"))
dim(glad)

edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
dim(edgi)

nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
dim(nbr)

ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
dim(ramp)
```

glad/edgi data frame list
```{r glad/edgi data frame list}
dat <- bind_rows(
  glad,
  edgi,
  nbr,
  ramp
)
```

```{r Skim data}
#look at the data
skimr::skim(dat)
```

```{r Save four cohorts as rds file}
saveRDS(object = dat, file = paste0(data_path, "/four_cohorts.rds"))
```

>>>>

# Import data
```{r import data}
coping_baseline <- read_rds(path = paste0(data_path, "/four_cohorts.rds"))
dim(coping_baseline)

cfs_wave6 <- read_rds(path = paste0(data_path, "/cfs_wave6.rds"))
dim(cfs_wave6)

```

```{r merge data frames}
dat <- left_join(
  coping_baseline,
  cfs_wave6, by = c("Sample", "ID")
)
```

```{r Skim data}
#look at the data 
#skimr::skim(dat) #(too big to run)
dim(dat)
```

```{r Save four cohorts as rds file}
saveRDS(object = dat, file = paste0(data_path, "/baseline_and_cfs_wave6.rds"))
```
